---
title: "interstroke_model_figure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{interstroke_model_figure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Welcome to the Interstroke R Package
Let's start exploring. The first thing to do is call the interstroke library.

```{r setup,warning=FALSE, message=FALSE}
library(interstroke)
```

# Create your model pointrange figure
The model pointrange figure creates a plot comparing estimates and CI's of multiple models. Estimates and CI's are plot against a log y-axis. The x-axis groups the models based on the source data grouping (quartile, quintile, etc). 

The function requires three arguments. 

The first argument (interstroke_data) is a dataframe containing the required variables. 

The second argument (models) contains a list of model formulas to be compared. 

The third agrumgent (regression_type) accepts either "unconditional" or "conditional". When using "conditional", model formulas must end in +strata(caseid). 

Example 1: We'll look at the quintiles of bmi unconditional model estimates. Comparing a base fit with an adjusted for age and sex fit.

```{r model_bmi_1, message = FALSE, fig.dim = c(8.5, 5), warning = FALSE}

is_figure_models(interstroke_data=interstroke_bmi, 
                 models=c(case_num~bmi_quintiles,case_num~bmi_quintiles+eage+esex),
                 regression_type = "unconditional")

```

Example 2: Conditional regression can be carried out by changing the regression_type parameter to "conditional". This requires the model to end in strata(caseid). 

```{r model_bmi_2, message = FALSE, fig.dim = c(8.5, 5), warning = FALSE}

is_figure_models(interstroke_data=interstroke_bmi, 
                 models=c(case_num~bmi_quintiles+strata(caseid),case_num~bmi_quintiles+eage+esex+strata(caseid)),
                 regression_type = "conditional")

```
Example 3: Reference groups for analysis should appear first and will follow the levels defined in the DATASET script. 

```{r model_bmi_3, message = FALSE, fig.dim = c(8.5, 5), warning = FALSE}

is_figure_models(interstroke_data=interstroke_bmi,
                 models=c(case_num~smoking+strata(caseid),case_num~smoking+eage+esex+whr+strata(caseid)),
                 regression_type = "conditional")

```

# Output to Microsoft Word

In R Studio click, Knit to Word.
