---
title: "interstroke_proportion_figure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{interstroke_proportion_figure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Welcome to the Interstroke R Package
Let's start exploring. The first thing to do is call the interstroke library.

```{r setup,warning=FALSE, message=FALSE}
library(interstroke)
```

# Create your proportion figure
The proportions figure creates a stacked bar plot illustrating the proportions of a predictor variable (y-axis) across collected categories (x-axis), split by cases and controls. 

The function requires at least three arguments. 

The first argument (interstroke_data) is a dataframe containing the required variables. 

The Second argument (x_axis_variable) is a categorical variable that will be split across the x-axis by cases and controls.

The third argument (proportion_variable) is the proportional variable that shows the proportional split within each categories cases & controls. 

Optional arguments may be provided for the following:

dropped_prop_levels: To exclude named levels of the predictor variable from the plot, assign a collection of the variables labels to exclude to "dropped_prop_levels". e.g.  dropped_prop_levels = c("BMI <25").

na_rm: To drop NA's from the analysis, use the na_rm logical argument, default is set to FALSE.

text_size: Assign a text size. Default is text_size = 3.7.

Example 1: We'll look at the proportional split of BMI by regions using the is_proportion_figure function.

```{r proportion_figure_bmi, message = FALSE, fig.dim = c(10, 5.5), warning = FALSE}

# is_figure_proportion(interstroke_data, x_axis_variable, y_axis_variable)

is_figure_proportion(interstroke_bmi, regionnn7, bmi_3_level)

```

Example 2: To filter named predictor levels. Create a collection of levels to exclude assigned to "dropped_prop_levels". 
Here we also exclude NA values using the na_rm = TRUE argument. 

```{r proportion_figure_bmi_dropvar, message=FALSE, fig.dim = c(10, 5.5)}

# Exclude BMI<25 and NA's
is_figure_proportion(interstroke_bmi, regionnn7, bmi_3_level, 
                     dropped_prop_levels = c("BMI <25"), na_rm = TRUE)

```

Example 3: We'll look at the proportional split of abdominal obesity (waist-to-hip ratio) by regions.

```{r proportion_figure_whr, message=FALSE, fig.dim = c(10, 5.5)}

is_figure_proportion(interstroke_proxy, regionnn7, highwhr)

```

Example 4: Example 3 with exclusions and dropped NA's. Notice the y-axis will automatically adjust if all proportions are low.

```{r proportion_figure_whr2, message=FALSE, fig.dim = c(10, 5.5)}

#Exclude NA's, Low and Moderate whr's.
is_figure_proportion(interstroke_proxy, regionnn7, highwhr,
                     dropped_prop_levels = c("Low", "Moderate"), na_rm = TRUE)

```


# Output to Microsoft Word

In R Studio click, Knit to Word.
