---
title: "interstroke_forest_plot"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{interstroke_forest_plot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Welcome to the Interstroke R Package
Let's start exploring. The first thing to do is call the interstroke library.

```{r setup,warning=FALSE, message=FALSE}
library(interstroke)
```

# Create standard deviation data from continous variable

Forest plots can compare the odds ratio for 1 standard deviation increase. 

To create a standard deviation variable, create a new column in your interstroke_data dataframe similar to the following:

```{r sd_data}

## Using whr, create a whr_z by subtracting the mean from each value and dividing by the standard deviation
interstroke_bmi$whr_z <- (interstroke_bmi$whr - mean(interstroke_bmi$whr, na.rm = TRUE)) / 
  sd(interstroke_bmi$whr, na.rm = TRUE)

```


# Create your forest plot
is_figure_stratified_subgroups creates an odds ratio forest plot comparing estimates and CI's between subgroups. Estimates and CI's are plot against a log odds x-axis. The y-axis is split into subgroups. 

The function requires three arguments. 

The first argument (interstroke_data) is a dataframe containing the required variables. 

The Second argument (subgroups) is a collection of categorical variables to display along the y-axis. Format = c("subgroup_level1", "subgroup_level2"...)

The third argument (model) contains the model to be fitted. 

The fourth argument (regression_type) accepts either "unconditional" or "conditional". When using "conditional", model formulas must end in +strata(caseid). 

Optional arguments may be provided for the following:

include_overall: Overall analysis is included by default and can be disabled by supplying the "include_overall = FALSE" argument. 

p_sig: By default, all p values under 1 will be displayed. Assign a p_sig value of your choosing to only display p values significant to this level. 

limits: Set plot axis limits in the format limits = c(0,10)

breaks: Manually assign axis tick breaks. format: breaks = seq(0, 100, by = 20)

long_title: Default as TRUE, will print a descriptive title. Set to FALSE to display just the predictor as the title. 

text_size: Assign a text size. Default is text_size = 4.

Example 1: Unconditional 

```{r forest_data, message = FALSE, fig.dim = c(10, 8), warning = FALSE, results='hide'}

is_figure_stratified_subgroups(interstroke_data = interstroke_pollution,
                                        subgroups = c("esex","smoking","antihypertpre","cardiacrfcat"),
                                        model = case_num~sysbp,
                                        regression_type = "unconditional")

```

Example 2: No overall and predictor as title. 

```{r forest_data2, message = FALSE, fig.dim = c(10, 8), warning = FALSE, results='hide'}

is_figure_stratified_subgroups(interstroke_data = interstroke_bmi,
                                           subgroups = c("esex","smoking","alcohfreqcat","antihypertpre","cardiacrfcat"),
                                           model = case_num~whr_z,
                                           regression_type = "unconditional",
                                           include_overall = FALSE,
                                           long_title = FALSE)

```

Example 3: Conditional variant of example 2. Change regression type to "conditional" and append strata(caseid) to the end of the model.

```{r forest_data3, message = FALSE, fig.dim = c(10, 8), warning = FALSE, results='hide'}

is_figure_stratified_subgroups(interstroke_data = interstroke_bmi,
                                           subgroups = c("esex","smoking","alcohfreqcat","antihypertpre","cardiacrfcat"),
                                           model = case_num~whr_z+strata(caseid),
                                           regression_type = "conditional",
                                           include_overall = FALSE,
                                           long_title = FALSE)

```

# Output to Microsoft Word

In R Studio click, Knit to Word.
