---
title: "interstroke_subtypes_figure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{interstroke_subtypes_figure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Welcome to the Interstroke R Package
Let's start exploring. The first thing to do is call the interstroke library.

```{r setup,warning=FALSE, message=FALSE}
library(interstroke)
```

# Create your stroke type subtype pointrange figure
The subtype pointrange figure creates a plot comparing estimates and CI's of a model across stroke types (All stroke, Ischaemic and ICH). Estimates and CI's are plot against a log y-axis. The x-axis groups the models based on stroketype. 

The function requires three arguments. 

The first argument (interstroke_data) is a dataframe containing the required variables. 

The second argument (model) is a model formula to be compared across stroke types.

The third argument (regression_type) accepts either "unconditional" or "conditional". When using "conditional", model formulas must end in +strata(caseid). 

Example 1: We'll look at the quintiles of bmi model estimates across stroke types using unconditional regression.

```{r subtype_bmi_1, message = FALSE, fig.dim = c(8.5, 5), warning = FALSE}

is_figure_subtypes(interstroke_data=interstroke_bmi, 
                   model=case_num ~ bmi_quintiles,
                   regression_type = "unconditional")

```

Example 2: We'll look at the quintiles of bmi model estimates across stroke types using conditional regression (add strata(caseid) to the end of model).

```{r subtype_bmi_2, message = FALSE, fig.dim = c(8.5, 5), warning = FALSE}

is_figure_subtypes(interstroke_data=interstroke_bmi, 
                   model=case_num ~ bmi_quintiles + strata(caseid),
                   regression_type = "conditional")

```

Example 3: Reference groups for analysis should appear first and will follow the levels defined in the DATASET script. 

```{r subtype_bmi_3, message = FALSE, fig.dim = c(8.5, 5), warning = FALSE}

is_figure_subtypes(interstroke_data=interstroke_bmi,
                   model=case_num ~ smoking + strata(caseid),
                   regression_type = "conditional")

```

# Output to Microsoft Word

In R Studio click, Knit to Word.

