---
title: "interstroke_mrs_figure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{interstroke_mrs_figure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Welcome to the Interstroke R Package
Let's start exploring. The first thing to do is call the interstroke library.

```{r setup,warning=FALSE, message=FALSE}
library(interstroke)
```

# Create your Modified Rankin Scale (MRS) figure
The Modified Rankin Scale figure creates a horizontal stacked bar plot illustrating the distribution of modified rankin scale across a variable.

The function requires at least three arguments. 

The first argument (interstroke_data) is a dataframe containing the required variables. 

The Second argument (x_axis_variable) is a categorical variable that divides the population into groups of the variables level.

Optional arguments may be provided for the following:

dropped_prop_levels: To exclude named levels of the predictor variable from the plot, assign a collection of the variables labels to exclude to "dropped_prop_levels". e.g.  dropped_prop_levels = c("BMI <25").

na_rm: To drop NA's from the analysis, use the na_rm logical argument, default is set to FALSE.

text_size: Assign a text size. Default is text_size = 3.7.

Example 1: We'll look at the MRS distribution by the csdiffsl variable (difficulty getting to sleep) using the is_figure_mrs function.

```{r is_figure_mrs_csdiffsl, message = FALSE, fig.dim = c(10, 5.5), warning = FALSE}

is_figure_mrs(interstroke_sleep %>% drop_na(csdiffsl) %>% filter(case== "Case"),csdiffsl)

```


# Output to Microsoft Word

In R Studio click, Knit to Word.
