---
title: "interstroke_table_two"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{interstroke_table_two}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Welcome to the Interstroke R Package
Let's start exploring. The first thing to do is call the interstroke library.

```{r setup, warning=FALSE, message=FALSE}
library(interstroke)
```

# Create your Interstroke Table Two

The first argument (interstroke_data) is a dataframe containing the required variables. 

The second argument (models) contains a list of model formulas to be compared. 

The third agrumgent (regression_type) accepts either "unconditional" or "conditional". When using "conditional", model formulas must end in +strata(caseid). 

Optional arguments may be provided for the following:

table_title: Override the default title with a custom title in the format: table_title = "Custom title".

Example 1: Unconditional association between cookplace and stroke.

```{r table_two_example1, message=FALSE}

is_table_two(interstroke_data=interstroke_pollution,
             models=c(case_num~cookplace,case_num~cookplace+eage+nevfcur+aheiscore+whrs2tert+hhincome+cardiacrfcat+sysbp+education,
                      case_num~cookplace+eage+nevfcur+aheiscore+whrs2tert+hhincome+cardiacrfcat+sysbp+education+country+incomectry),
             regression_type="unconditional")

```

Example 2: Conditional association between smoking and stroke.

```{r table_two_example2, message=FALSE}

is_table_two(interstroke_data=interstroke_bmi,
             models=c(case_num~smoking+strata(caseid),
                      case_num~smoking+eage+nevfcur+aheiscore+whrs2tert+hhincome+cardiacrfcat+sysbp+strata(caseid),
                      case_num~smoking+eage+nevfcur+aheiscore+whrs2tert+hhincome+cardiacrfcat+sysbp+incomectry+strata(caseid)),
             regression_type="conditional")

```
# Output to Microsoft Word

In R Studio click, Knit to Word.
