---
title: "interstroke_table_one"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{interstroke_table_one}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Welcome to the Interstroke R Package
Let's start exploring. The first thing to do is call the interstroke library.

```{r setup, warning=FALSE, message=FALSE}
library(interstroke)
```

# Create your first Interstroke Table One
"Table one's" contain baseline values of collected variables (rows) across an important predictor variable. For this example, we'll look at the baseline collected variables across different levels of pollution at home using the is_table_one function.

The first argument (interstroke_data) is a dataframe containing the required variables. 

The second argument (model) is the standard R formula. The left hand side of the ~ symbol contains the predictor (placed on the columns in the table) and the right hand side contains the baseline variables (placed on the rows of the table).

```{r table_one, message=FALSE, warning=FALSE}

is_table_one(interstroke_data=interstroke_pollution, 
             model = polluteh~eage+bmi+sysbp)

```

# Output to Microsoft Word

In R Studio click, Knit to Word.
